\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/relatedwork.tex
minor changes: grammar in iteration3, line separater in relatedwork
Strip trailing spaces
intro shortened
relatedwork: more CV citations + minor updates

\subsection{Head and Gaze Input}
Head movement has long been used for virtual camera control in VR applications~\cite{pausch_user_1993} and as an assistive input technology for cursor control of desktop applications~\cite{radwin1990method}. However, human neck muscles have a lower bandwidth than other muscle groups, e.g., the wrist~\cite{card_morphological_1991}.

%Card, summarizing other work, shows that neck muscles are a poor muscle group for pointing in general: neck muscles only have a bandwidth of about $4.2bits/s$ (compared to $23bits/s$ of wrist muscles used by a standard mouse~\cite{Card:1991:MAD:123078.128726}.

Prior work often focused on head orientation for controlling graphical interfaces; in contrast, we apply this modality to selection in physical spaces.

@@

\subsection{Pointing in Physical Spaces}
Rukzio studied alternative methods for selecting devices in physical spaces and found that users strongly preferred either tapping target appliances with a mobile device or pointing at a distance to browsing a list~\cite{rukzio_experimental_2006}.

@@

Handheld projectors can both display a user interface in space and communicate control information optically, e.g., by encoding information temporally (using Gray codes in Picontrol~\cite{schmidt_picontrol:_2012} and RFIG Lamps~\cite{raskar_rfig_2004}) or spatially (using QR codes in the infrared spectrum in SideBySide~\cite{willis_sidebyside:_2011}). Our solution is similar in spirit but relies on simple low-cost IR emitters and detectors. \bjoern{need a stronger statement here}
%However, visible tags at appropriate sizes may be rejected by users because of their negative aesthetic effect on the space.

@@

\subsection{Markers and Vision Methods}
\achal{Not sure where to put this, feel free to move.}
\ben{For CV, I think related work is one option to go; however, the requirement of being related work is that -- we need to reference them. There are a few examples ``require large, obtrusive tags, and inevitably lack feedback from passive devices in the environment'' which should be referenced. That's why I am thinking of putting this to discussion.}
\changes{Many alternative solutions for detecting devices in contained spaces
rely on passive tags on devices, combined with computer vision methods for
detection. Unfortunately, these methods either impose significant constraints
on the camera used for detection, or require large, obtrusive tags, and
inevitably lack feedback from passive devices in the environment. \cite{Bokode},
for example, relies on visually imperceptible codes, but has significant
drawbacks: despite using a 12.1 megapixel DSLR camera, detections are no
longer robust past an angle of 20. Similarly, in our experiments, we found
that striking a balance between the size of the tag, the prices of the
device, and the computational cost of detection was unfeasible with current
cameras and algorithms.}

>>>>

\subsection{Head and Gaze Input}
Head movement has long been used for virtual camera control in VR applications~\cite{pausch_user_1993} and as an assistive input technology for cursor control of desktop applications~\cite{radwin1990method}. However, it is notable that human neck muscles have a lower bandwidth than other muscle groups, e.g., the wrist~\cite{card_morphological_1991}.
%
%Card, summarizing other work, shows that neck muscles are a poor muscle group for pointing in general: neck muscles only have a bandwidth of about $4.2bits/s$ (compared to $23bits/s$ of wrist muscles used by a standard mouse~\cite{Card:1991:MAD:123078.128726}. 
%
Prior work often focused on head orientation for controlling graphical interfaces; in contrast, we apply this modality to selection in physical spaces.

@@

\subsection{Pointing in Physical Spaces}
Rukzio ~\cite{rukzio_experimental_2006} studied alternative methods for selecting devices in physical spaces and found that users strongly preferred either tapping target appliances with a mobile device or pointing at a distance to browsing a list.

@@

Handheld projectors can both display a user interface in space and communicate control information optically, e.g., by encoding information temporally (using Gray codes in Picontrol~\cite{schmidt_picontrol:_2012} and RFIG Lamps~\cite{raskar_rfig_2004}) or spatially (using QR codes in the infrared spectrum in SideBySide~\cite{willis_sidebyside:_2011}). Our solution is similar in spirit but requires only small, low-cost IR emitters and detectors. \bjoern{need a stronger statement here} \achal{Tried to add a small contrast of small/low cost, but don't want to explicitly say projectors are large and unwieldy as there may be some exceptions.}
%However, visible tags at appropriate sizes may be rejected by users because of their negative aesthetic effect on the space.

@@

\subsection{Markers and Vision Methods}
\achal{Not sure where to put this, feel free to move.}

\ben{For CV, I think related work is one option to go; however, the requirement of being related work is that -- we need to reference them. There are a few examples ``require large, obtrusive tags, and inevitably lack feedback from passive devices in the environment'' which should be referenced. That's why I am thinking of putting this to discussion.}

\changes{Many alternative solutions for detecting devices in contained spaces
rely on passive tags on devices, combined with computer vision methods for
detection. Unfortunately, these methods impose significant constraints
on the camera used for detection~\cite{Bokode}, require large, obtrusive tags, or are
designed to work specifically at short distances~\cite{CyberCode}; inevitably,
they also lack feedback from passive devices in the environment. \cite{Bokode},
for example, relies on visually imperceptible codes, but has significant
drawbacks: despite using a 12.1 megapixel DSLR camera, detections are no longer
robust past an angle of 20. Similarly, in our experiments, we found that
striking a balance between the size of the tag, the prices of the device, and
the computational cost of detection was unfeasible with current cameras and
algorithms.}
